Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-06 paper/abstract.tex
Batched => Batch

\begin{abstract} 
    The Bayesian optimization algorithm has recently shown promising
    performance for the automated design analog integrated circuits. However,
    the sequential property of Bayesian optimization limits its further
    application. In this paper, a batched bayesian optimization algorithm is
    proposed, the parallelization is realized via a multi-objective ensemble of
    acquisition functions. In each iteration, multiple acquisition functions
    are selected, the multi-objective optimization is performed to search for
    the Pareto front of the acquisition functions, candidate points are then
    sampled from the Pareto front. The proposed method is compared with several
    state-of-the-art batched Bayesian optimization algorithms using analytical
    benchmark functions and real-world analog circuits; the experimental
    results show that the proposed method is competitive compared to the
    state-of-the-art algorithms.
\end{abstract}

>>>>

\begin{abstract} 
    The Bayesian optimization algorithm has recently shown promising
    performance for the automated design analog integrated circuits. However,
    the sequential property of Bayesian optimization limits its further
    application. In this paper, a batch bayesian optimization algorithm is
    proposed, the parallelization is realized via a multi-objective ensemble of
    acquisition functions. In each iteration, multiple acquisition functions
    are selected, the multi-objective optimization is performed to search for
    the Pareto front of the acquisition functions, candidate points are then
    sampled from the Pareto front. The proposed method is compared with several
    state-of-the-art batch Bayesian optimization algorithms using analytical
    benchmark functions and real-world analog circuits; the experimental
    results show that the proposed method is competitive compared to the
    state-of-the-art algorithms.
\end{abstract}

### 2018-02-06 paper/conclusion.tex
Paper update
Batched => Batch

In this paper, a batched Bayesian optimization algorithm is proposed for the
automation of analog circuit design. the parallelization is achieved via
multi-objective ensemble of acquisition function. In each iteration, the
candidate points are sampled from the Pareto front of multiple acquisition
functions. We compared the proposed MACE algorithm using analytical benchmark
functions and real-world circuits, it is shown that the MACE algorithm is
competitive compared with state-of-the-art method listed in the paper.

>>>>

In this paper, a batch Bayesian optimization algorithm is proposed for the
automation of analog circuit design. The parallelization is achieved via
the multi-objective ensemble of acquisition function. In each iteration, the
candidate points are sampled from the Pareto front of multiple acquisition
functions. We compared the proposed MACE algorithm using analytical benchmark
functions and real-world circuits, it is shown that the MACE algorithm is
competitive compared with state-of-the-art method listed in the paper.

### 2018-02-06 paper/experiments.tex
Batched => Batch

The mean convergence plot is shown in Figure~\ref{fig:CovPlotBenchmark}. The
statistics of the final optimization results are listed in
Table~\ref{tab:result_analytical}. As can be seen, when running with batch size
$B = 4$, the MACE algorithm gives the best performance for six out of the eight
benchmarks.  For the 2D Ackley function, EI-LP is the best algorithm, while for
the Eggholder function, the MACE, BLCB, and EI-LP have quite similar
performance.  Compare the batched MACE and the sequential MACE, the speedup is
also dramatic.

@@

We run the algorithms in sequential mode and batched mode, for the batched
mode, batch size is set to $B = 4$. The number initial random sampling is set
to $N_{init} = 100$, and the number of iterations is set to $N_{iter} = 100$.

@@

The mean convergence plot for the sequential and batched runs are plotted in
Figure~\ref{fig:resDAC2014}. As can be seen, the MACE algorithm gave better
solution compared to other algorithms, the sequential MACE algorithm found
better solution than BLCB and EI-LP with batch size $B = 4$, which showed that
the multi-objective acquisition ensemble is more robust than relying on single
acquisition function; compared to the sequential MACE algorithm, the MACE
algorithm with batch size $B = 4$ showed considerable speedup.

@@

The MACE, BLCB, and EI-LP algorithms were tested in both sequential and batched
mode. The number of initial sampling is $N_{init} = 100$, the number of
iterations is $N_{iter} = 100$, the batch size is set to $B = 4$, so the total
number of HSPICE simulations is 500 for each batched run and 200 for each
sequential run.

@@

The mean convergence plot is given in Figure~\ref{fig:resClassE}. We can see
that the MACE outperformed the BLCB and EI-LP in both sequential and batched
mode. For the batched runs, the MACE convergences fastest among the three
algorithms, while the sequential MACE has similar performance as the batched
EI-LP method.

>>>>

The mean convergence plot is shown in Figure~\ref{fig:CovPlotBenchmark}. The
statistics of the final optimization results are listed in
Table~\ref{tab:result_analytical}. As can be seen, when running with batch size
$B = 4$, the MACE algorithm gives the best performance for six out of the eight
benchmarks.  For the 2D Ackley function, EI-LP is the best algorithm, while for
the Eggholder function, the MACE, BLCB, and EI-LP have quite similar
performance.  Compare the batch MACE and the sequential MACE, the speedup is
also dramatic.

@@

We run the algorithms in sequential mode and batch mode, for the batch
mode, batch size is set to $B = 4$. The number initial random sampling is set
to $N_{init} = 100$, and the number of iterations is set to $N_{iter} = 100$.

@@

The mean convergence plot for the sequential and batch runs are plotted in
Figure~\ref{fig:resDAC2014}. As can be seen, the MACE algorithm gave better
solution compared to other algorithms, the sequential MACE algorithm found
better solution than BLCB and EI-LP with batch size $B = 4$, which showed that
the multi-objective acquisition ensemble is more robust than relying on single
acquisition function; compared to the sequential MACE algorithm, the MACE
algorithm with batch size $B = 4$ showed considerable speedup.

@@

The MACE, BLCB, and EI-LP algorithms were tested in both sequential and batch
mode. The number of initial sampling is $N_{init} = 100$, the number of
iterations is $N_{iter} = 100$, the batch size is set to $B = 4$, so the total
number of HSPICE simulations is 500 for each batch run and 200 for each
sequential run.

@@

The mean convergence plot is given in Figure~\ref{fig:resClassE}. We can see
that the MACE outperformed the BLCB and EI-LP in both sequential and batch
mode. For the batch runs, the MACE convergences fastest among the three
algorithms, while the sequential MACE has similar performance as the batch
EI-LP method.

### 2018-02-06 paper/intro.tex
Batched => Batch

% TODO: Review current methods
% TODO: See how other papers review existing batched BO methods
Batched Bayesian optimization has been a hot topic in the BO literature.
Related works include the simulation matching (SM)
method~\cite{azimi2010batch}, the BUCB (BLCB for minimization)
method~\cite{desautels2014parallelizing}, the GP-UCB-PE
method~\cite{contal2013parallel}, the local penalization (LP)
method~\cite{gonzalez2016batch}, the parallel predictive entropy (PPES)
search~\cite{shah2015parallel} and the qKG method~\cite{wu2016parallel}.

@@

In this paper, we propose to parallelize the Bayesian optimization algorithm
via the multi-objective acquisition ensemble (MACE). Firstly, in each
iteration, after the GP model is updated, multiple acquisition functions are
selected, we then perform multi-objective optimization to find the \emph{Pareto
front} (PF) of the acquisition functions. The PF represents the best trade-off
between these acquisition functions. When batched evaluations are possible, we
can sample multiple points on the optimized PF to accelerate the optimization.

>>>>

% TODO: Review current methods
% TODO: See how other papers review existing batch BO methods
Batch Bayesian optimization has been a hot topic in the BO literature.
Related works include the simulation matching (SM)
method~\cite{azimi2010batch}, the BUCB (BLCB for minimization)
method~\cite{desautels2014parallelizing}, the GP-UCB-PE
method~\cite{contal2013parallel}, the local penalization (LP)
method~\cite{gonzalez2016batch}, the parallel predictive entropy (PPES)
search~\cite{shah2015parallel} and the qKG method~\cite{wu2016parallel}.

@@

In this paper, we propose to parallelize the Bayesian optimization algorithm
via the multi-objective acquisition ensemble (MACE). Firstly, in each
iteration, after the GP model is updated, multiple acquisition functions are
selected, we then perform multi-objective optimization to find the \emph{Pareto
front} (PF) of the acquisition functions. The PF represents the best trade-off
between these acquisition functions. When batch evaluations are possible, we
can sample multiple points on the optimized PF to accelerate the optimization.
